\begin{rubric}{\makefield{\faSuitcase}{Professional Experiences}}


\entry*[2023 - present]%
	\textbf{Team lead \& Python Developer} \par {\emph ParsTech.Co}
        \begin{itemize}
          \setlength{\itemsep}{0ex} % Adjust the space between items
          \setlength{\parskip}{1pt}     % Adjust the space between paragraphs within an item
          %\setlength{\itemindent}{-1em}
            \item Introduced and programmed a graph-based workflow to create a user-defined dialogue flow for a personalized chatbot that can be customized with LLMs and RAGs.
            \item Leveraged asynchronous I/O to enhance server capacity and reduce response times.
            \item Improved multi-processing, multi-threading, and asynchronous programming skills of 12 of my coworkers.
        \end{itemize}


\entry*[2021 -- 2023]%
	\textbf{ML Engineer \& Backend Developer} \par {\emph ParsTech.Co}
        \begin{itemize}
          \setlength{\itemsep}{0ex} % Adjust the space between items
          \setlength{\parskip}{1pt}     % Adjust the space between paragraphs within an item
          %\setlength{\itemindent}{-1em}
          \item Optimized RAM and CPU of the camera streaming service by about 30\%.
          \item Implemented a streaming service that can connect to 25 HD cameras with 12 cores CPU and 2.5 GB RAM to proceed 20 frames per second.
          \item Integrated a system for detecting personal protective equipment with 4 cameras capable of 5 categories.
          \item Developed a task-oriented framework to deal with ML models and pipelines in the production environments.
          \item Dockerized 3 AI and 5 Backend services to run reliably and securely in any infrastructure.
          \item Trained 5 of my co-workers to lead the different product services.
        \end{itemize}



\entry*[2020 -- 2021]%
	\textbf{Machine Learning Engineer} \par {\emph TaraTech.Co}

        \begin{itemize}
          \setlength{\itemsep}{0ex} % Adjust the space between items
          \setlength{\parskip}{1pt}     % Adjust the space between paragraphs within an item
            \item  Designed a pipeline containing 5 ML models (object detection, layout composition, pose detection, depth estimation, and image blending) for human localization on the background image.
            \item Trained an ACGAN model on the heart disease dataset to augment the data which achieved 70\% accuracy in generating fake data.
        \end{itemize}
        
\entry*[2019 -- 2020]% 
	\textbf{Internship} \par {\emph Telecommunication Company of Iran} 


\end{rubric}