\begin{rubric}{\makefield{\faFolderOpen}{Projects}}
% \subrubric{Awards and Achievements}

\entry*[2022 - present] \textbf{\Large Parstech Video Intelligent Assistant}
        \par \emph{\large Intelligent Security Assistant}
        \par AI assistance to process and analyze videos with modules like human detection, face recognition, and license plate recognition. I deeply worked on human detection and restriction area application, Camera handling and streaming, DevOps, and microservices of this application.

            \par \textbullet \hspace{1em} Human detection and tracking
            \par \textbullet \hspace{1em} Video Processing with OpenCV
            \par \textbullet \hspace{1em} FastAPI implementation for APIs
            \par \textbullet \hspace{1em} Gstreamer and OpenCV cores for the Camera management service

            \par \textbullet \hspace{1em} Task queueing and workflow management with Celery
            \par \textbullet \hspace{1em} Containerized services
            \par \textbullet \hspace{1em} In-Memory data transfer with Redis and python shared memory
            \par \textbullet \hspace{1em} Multi-Processing and Multi-Threading features implemented

        

\entry*[2022] \textbf{\Large LipReading model on Persian Dataset}  
        
        \par Train a LipReading model on the Persian dataset.

\entry*[2021] \textbf{\Large Personal Protective Equipment (PPE)} 
        \par \emph{Implementation of a system to identify personal safety equipment}
        \par A program to identify workers' safety equipment in workshop and construction environments, such as gloves, helmets, glasses, masks, safety vests, warning capabilities for people who enter prohibited areas, fire detection, and identification of work tools.

            \par \textbullet \hspace{1em}  Human detection and tracking
            \par \textbullet \hspace{1em}  Pose estimation to check human body status 
            \par \textbullet \hspace{1em}  Body part localizer for head, hands, and chest
            \par \textbullet \hspace{1em}  Equipment classifiers models
            \par \textbullet \hspace{1em}  Pipeline implementation to estimate human fall
            \par \textbullet \hspace{1em}  Faster functions with numba jit compiler


\entry*[2021] \textbf{\Large Pressure Ulcer} 
        \par Analysis of pressure sensor data of hospital beds for prediction and diagnosis of bed sores.
        

            \par \textbullet \hspace{1em}  Body Segmentation Models.
            \par \textbullet \hspace{1em}  Pose estimation model for pressure sensor data
            \par \textbullet \hspace{1em}  Video processing with OpenCV
            \par \textbullet \hspace{1em}  Signal Capturing from human poses
        

\entry*[2021] \textbf{\Large Cardiac Medical Data Augmentation}
        \par Train ACGAN on real Cardiac Medical Data in order to generate fake data for augmentation.



\entry*[2021] \textbf{\Large Human localization}
        \par In two categories of foreground and background images, it takes a personal image from the foreground, and in order to place it in the background image, it first finds the right place then masks the image and places it in the background, and then corrects the color and light also improves the image by a model.

            \par \textbullet \hspace{1em}  Depth Estimation 
            \par \textbullet \hspace{1em}  Image brightness correction \& Color correction models
            \par \textbullet \hspace{1em}  Object detection models to find humans and other objects in the Image.
            \par \textbullet \hspace{1em}  Image Perspective calculation
            \par \textbullet \hspace{1em}  Image blending
      

\entry*[2021] \textbf{\Large OCR}
        \par Optical Character Recognition on German administrative forms.

            \par \textbullet \hspace{1em}  Use tesseract and self-trained text recognition neural network.
            \par \textbullet \hspace{1em}  Use Clustering algorithms to find lines.
            \par \textbullet \hspace{1em}  Use OpenCV and Image processing methods to find information blocks.

\end{rubric}